Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-10 chapters/analysis_techniques.tex
Changes 1. Added conclusion in final remarks 2. Added hysteresis curve for prolate particles stabilized bijels in aim2 section 3. Added description of synthesis techniques in lit review
adding references in shear banding methods section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

The nematic order parameter is calculated from the orientational alignment tensor, $Q$, which is calculated from the 
orientation of particles to one another as 
$\langle Q \rangle = \frac{1}{N} \sum_{i}^{N} \langle \frac{3}{2}u_i u_i - \frac{1}{2}I \rangle$. $u_i$ is the 
orientation of particle $i$ and $I$ is an identity matrix. \cite{veerman_phase_1992} While there are multiple 
methods to evaluate the nematic order parameter, the one we have picked is where the largest eigenvector is $S$, 
with its corresponding eignvector referring to the director of the system. \cite{veerman_phase_1992} 
\textcolor{blue}{https://doi.org/10.1080/00268978400101951} A system is defined to be ordered nematically, 
if $S > 0.3$. In this work, the direction of the director will be compared to the direction of the magnetic 
field. We utilize the implementation in Freud to calculate the nematic order parameter.

@@

In the literature, crystal structures can be distinguished from one another by plotting the distribution of two or more $Q_{l}$.

\subsection{Shear viscosity}
\label{section:shear_viscosity}

Shear viscosity is a physical parameter measured through the dissipation of applied strain onto a fluid, resulting in 
an applied shear stress. In an incompressible fluid, the viscosity $(\eta)$ is defined as the ratio between the measured 
shear stress $(\sigma)$ and the applied strain rate $(\dot{\gamma})$, $\sigma = \eta \dot{\gamma}$. In rheological 
experiments, the shear viscosity is measured through a viscometer based on Couette or shear viscometry and Poiselle or 
pressure gradient viscometry. A Couette cell functions by applying a shear velocity to one or more walls, and measuring 
the shear stress response of the fluid. Common geometries for Couette cells include the cone and plate and concentric 
cylinder viscometers.

In this work, a shear velocity is imparted in the z direction, across the x-axis. Therefore, the shear stress in the x 
and z directions, $\sigma_{xz}$, is measured. $\sigma_{xz}$ is output per lattice in the output file, which is then 
averaged across the entire volume to obtain an average shear stress $\hat{\sigma_{xz}}$. The effective viscosity of the 
system, $\eta_{eff}$ is calculated using $\eta_{eff} = \frac{\hat{\sigma_{xz}}}{\dot{\gamma}}$ where $\dot{\gamma} = 
\frac{2 u_{LE}}{L_x}$. $u_{LE}$ is the shear velocity is enforced through the Lees-Edwards boundary condition, as 
described in section \textcolor{blue}{description of lees edwards BC}.

\subsection{Yield stress and zero shear rate viscosity}
\label{section:yield_stress}

The yield stress of bijels can be calculated using the flow curve, stress ramp or from oscillatory rheological techniques. 
The flow curve method involves the steady application of shear, followed by measurements of the shear stress response of 
the material. The plateau of the shear stress response is indicative of the yield stress of the material. The stress ramp 
method involves the application of a shear stress onto the material, followed by measurements of the strain rate. A 
perfectly elastic material will have no strain rate, while a perfectly disspitative material will have high strain rate. 
The yield stress is characterized as the point when a rapid increase in strain rate is observed. The yield stress from 
oscillatory rheology is defined when the storage modulus is lower than the loss modulus. This work will utilize the flow 
curve method.

The shear viscosity calculated using the method detailed in Section \ref{section:shear_viscosity} will be plotted as a 
function of applied shear rate. Rheological models such as the Herschel Buckley, Bingham Plastic or Carreu models can be 
utilized to fit the shear viscosity as a function of shear rate to calculate the zero shear rate viscosity. In bijel 
applications, this parameter gives insight into the material stability and processability.

\subsection{Shear banding}
\label{section:shear_banding}

>>>>

The nematic order parameter is calculated from the orientational alignment tensor, $Q$, which is calculated from the 
orientation of particles to one another as 
$\langle Q \rangle = \frac{1}{N} \sum_{i}^{N} \langle \frac{3}{2}u_i u_i - \frac{1}{2}I \rangle$. $u_i$ is the 
orientation of particle $i$ and $I$ is an identity matrix. \cite{veerman_phase_1992} While there are multiple 
methods to evaluate the nematic order parameter, the one we have picked is where the largest eigenvector is $S$, 
with its corresponding eignvector referring to the director of the system. \cite{veerman_phase_1992} 
% \textcolor{blue}{https://doi.org/10.1080/00268978400101951} 
A system is defined to be ordered nematically, 
if $S > 0.3$. In this work, the direction of the director will be compared to the direction of the magnetic 
field. We utilize the implementation in Freud to calculate the nematic order parameter.

@@

In the literature, crystal structures can be distinguished from one another by plotting the distribution of two or more $Q_{l}$. 
\cite{lechner_accurate_2008, mickel_shortcomings_2013} Given that bijels form colloidal glasses, we only expect there to be
short range order which means conclusions made from this parameter can only be used to guide trends of order, not quantitative 
calculations of crystal structures.

\subsection{Shear stress}
\label{section:shear_viscosity}

In an incompressible fluid, the viscosity $(\eta)$ is defined as the ratio between the measured 
shear stress $(\sigma)$ and the applied strain rate $(\dot{\gamma})$, $\sigma = \eta \dot{\gamma}$. In rheological 
experiments, the viscosity is measured through a viscometer based on Couette or shear viscometry and Poiselle or 
pressure gradient viscometry. A Couette cell functions by applying a shear velocity to one or more walls, and measuring 
the shear stress response of the fluid. Common geometries for Couette cells include the cone and plate and concentric 
cylinder viscometers. In simulations, shear can be applied to walls of the simulation domain through either a shearing 
wall boundary condition or a Lees Edwards boundary condition. We select the Lees Edwards boundary condition as shearing 
results are unaffected by finite size effects and wall effects. Finite size effects are observed as a system size
dependent shear stress at the same shear rate. Wall effects can be seen as stick-slip effects of the particles or 
unphysical velocity gradients near the wall.

In a lattice boltzmann, the shear stress is measured as the sum of the equilibrium and nonequilibrium contributions.
\cite{kruger_shear_2009} These terms are defined as,

\begin{equation}
    \sigma_{\alpha \beta} = \sigma_{\alpha \beta}^{0} + \sigma_{\alpha \beta}^{1}
\end{equation}

This expression is obtained from the Chapman Enskog expansion of the lattice boltzmann method. The equilibrium and
non-equilibrium contributions of the stress are defined as

\begin{equation}
    \begin{split}
        \sigma_{\alpha \beta}^{0} &= \rho c_s^2 \delta_{\alpha \beta} + \rho u_{\alpha} u_{\beta} \\
        \sigma_{\alpha \beta}^{1} &= (1 - \frac{1}{2 \tau})\Sigma_{i} (f_{i} - f_{i}^{eq})c_{i \alpha}c_{i \beta} \\
    \end{split}
\end{equation}

In this work, a shear velocity is imparted in the z direction, across the x-axis. Therefore, the shear stress in the x 
and z directions, $\sigma_{xz}$, is measured. $\sigma_{xz}$ is output as calculated from the simulation for the entire 
domain after applying this equation to the system.

% \subsection{Yield stress and zero shear rate viscosity}
% \label{section:yield_stress}

% The yield stress of bijels can be calculated using the flow curve, stress ramp or from oscillatory rheological techniques. 
% The flow curve method involves the steady application of shear, followed by measurements of the shear stress response of 
% the material. The plateau of the shear stress response is indicative of the steady state stress of the material. The stress ramp 
% method involves the application of a shear stress onto the material, followed by measurements of the strain rate. A 
% perfectly elastic material will have no strain rate, while a perfectly dissipative material will have high strain rate. 
% The yield stress is characterized as the point when a rapid increase in strain rate is observed. The yield stress from 
% oscillatory rheology is defined when the storage modulus is lower than the loss modulus. This work will utilize the flow 
% curve method.

% The shear viscosity calculated using the method detailed in Section \ref{section:shear_stress} will be plotted as a 
% function of applied shear rate. Rheological models such as the Herschel Buckley, Bingham Plastic or Carreu models can be 
% utilized to fit the shear viscosity as a function of shear rate to calculate the zero shear rate viscosity. In bijel 
% applications, this parameter gives insight into the material stability and processability.

% \subsection{Shear banding}
% \label{section:shear_banding}

% \textcolor{blue}{https://doi.org/10.1073/pnas.0812519106}

% \textcolor{blue}{https://doi.org/10.1103/PhysRevX.11.021017}

### 2025-03-10 chapters/dissertation-tap.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

\begin{approvalpage}
\chair{Joshua Zide, PhD}{Chair of the Department of Materials Science and Engineering}
\dean{Jamie Phillips, PhD}{Dean of the College of Engineering}
\end{approvalpage}

@@

In the development of this dissertation, I extend my deepest gratitude to Dr Ulf Schiller whose support, motivation and 
opportunities have been indispensible during my PhD. I believe his approach to mentorship, methodical problem solving 
strategies, depth and breadth of knowledge have been invaluable sources of inspiration for this research as well as 
motivating myself to strive towards those ideals. I would also like to thank members of my committee, especially 
Dr Arthi Jayaraman from the University of Delaware and Dr Olga Kuksenok from Clemson University for their mentorship 
and motivation that pushed me to increase my breadth of knowledge and to think outside the box.

@@

Porous materials have found greater importance in applications such as water filtration, catalyst supports, battery 
electrodes and bio engineered materials. To accommodate a greater variety of pore sizes and continuous fabrication 
techniques with minimal waste, bottom up synthesis techniques have been gaining in popularity.

One such bottom up fabrication technique relies on jamming of particle stabilized emulsions into bicontinuous 
interfacially jammed emulsion gels(bijels). However, casting mixture independent microstructure control has not 
been identified, especially applicable in continuous bijel synthesis strategies such as Solvent Transfer Induced 
Phase separation. Stimuli response has been identified as a technique to enable this. This study focuses on utilizing 
stimuli response of bijels stabilized with ellipsoidal microparticles, and the resulting microstructure and rheological 
implications this induces.

We first identify that upon application of a field to a bijel stabilized with ellipsoidal particles during synthesis, 
microstructure change is observed, not present when analyzing bijels stabilized with spherical particles. Upon 
application of the field, particles reorient to the direction of the field, dragging the interface along with 
them. This causes the bijel to have axially dependent jamming, causing anisotropic microstructures to form.

@@

>>>>

\begin{approvalpage}
\chair{Joshua Zide, PhD}{Chair of the Department of Materials Science and Engineering}
\dean{Pamela M. Norris, PhD}{Dean of the College of Engineering}
\end{approvalpage}

@@

In the development of this dissertation, I extend my deepest gratitude to Dr Ulf Schiller whose support, motivation and 
opportunities have been indispensible during my PhD. I believe his methodical problem solving strategies, depth and 
breadth of knowledge have been invaluable sources of inspiration for me as well as 
motivating myself to strive towards those ideals. I would also like to thank members of my committee, 
from the University of Delaware and Clemson University for their mentorship 
and motivation that pushed me to increase my breadth of knowledge and to think outside the box.

@@

Porous materials have found great importance in applications such as water filtration, catalyst supports, battery 
electrodes and bio engineered materials. To accommodate a greater variety of pore sizes and continuous fabrication 
techniques with minimal waste, bottom up synthesis techniques have been gaining in popularity. One such technique is
emulsion templating of a specific microstructure known as a bicontinuous interfacially jammed emulsion gels(bijels).

However, casting mixture independent microstructure control is an open issue, especially applicable in continuous 
bijel synthesis strategies such as Solvent Transfer Induced Phase separation and as in-situ control mechanisms to
control the microstructure of a bijel to control properties such as separation efficiency. Stimuli response has been identified as a 
technique to enable this. This study focuses on utilizing stimuli response of bijels stabilized with ellipsoidal microparticles, 
and the resulting microstructure and rheological implications this induces.

We first identify that upon application of a field to a bijel stabilized with ellipsoidal particles during synthesis, 
microstructure change is observed, not present when analyzing bijels stabilized with spherical particles. Upon 
application of the field, particles reorient to the direction of the field, causing directional jamming that creates
microstructure anisotropy.

@@

Finally, we characterize that bijels retain their shear thinning behavior when analyzing the rheological response of bijels
under magnetic fields. We identify that the particle ordering plays a role in the evolution of the microstructure under shear
and the rheological response.

### 2025-03-10 chapters/model_params.tex
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

\section{Simulation setup}

@@

In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ 
used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the 
spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to 
$R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$. 
$R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
the particle respectively. These values are identical to what was used in Gunther et al, allowing comparisons to the 
trends they observed. \cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration
step was performed to push the particles further away from each after placement. Once equilibration is performed, a 
constant magnetic field is switched on with dimensionless strengths defined using $Bo_m$.

@@

Bijel templates have been synthesized using water/2-6-lutidine for further applications. \cite{lee_making_2013} 
While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently 
utilize small molecule liquids in their bijel casting mixtures. Therefore, an experimentally viable system using 
water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
for this system is $T_c = 37 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries 
by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
Comparing the physical properties to simulation parameters, the simulations correspond to a box side length of 
$L \approx 64.5 \mu m$ and a timestep duration of $\Delta t \approx 624 ns$.

\section{Model results}

\subsubsection{Surface tension}

In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed 
to break through the interface. Pendant drop tensionometry is also used by measuring the pressure required to 
maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the 
surface tension of the system. 
\textcolor{blue}{https://pubs.acs.org/doi/10.1021/la402436w, https://doi.org/10.1016/j.jcis.2015.05.012} 
Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between 
cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a 
system by increasing its size. For spherical droplets, the equation simplifies to 
$\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure 
between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension 
of the interface and $R_d$ is the radius of the droplet.

>>>>

\section{Simulation setup}
\label{section:sim_setup}

@@

In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ 
used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the 
spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to 
$R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$. 
$R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
the particle respectively. These values are identical to what was used in Gunther et al, allowing comparisons to the 
trends they observed. \cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration
step was performed to push the particles further away from each after placement. Once equilibration is performed, a 
constant magnetic field is switched on with dimensionless strengths defined using $\bar{B}$.

@@

Bijel templates have been synthesized using water/2-6-lutidine for further applications. \cite{lee_making_2013} 
While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently 
utilize small molecule liquids in their bijel casting mixtures. Therefore, an experimentally viable system using 
water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
for this system is $T_c = 34 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries 
by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
Comparing the physical properties to simulation parameters, the simulations correspond to a length scale of
$\Delta x = 252 \cdot 10^{-9} \text{m}$, timescale of $\Delta t = 624 \cdot 10^{-9} \text{s}$, 
mass scale of $\Delta m = 2.24 \cdot 10^{-15} \text{kg}$ and charge scale of $\Delta q = 2.948 \cdot 10^{-7} \text{C}$.

\section{Model results}
\label{section:model_results}

\subsection{Surface tension}
\label{section:model_surface_tension}

In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed 
to break through the interface. Pendant drop tensionometry is also used by measuring the pressure required to 
maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the 
surface tension of the system. \cite{sun_assembly_2013, berry_measurement_2015}
Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between 
cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a 
system by increasing its size. For spherical droplets, the equation simplifies to 
$\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure 
between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension 
of the interface and $R_d$ is the radius of the droplet.

### 2025-03-10 chapters/paper1.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/D2a-vs-B_ss.png}
\caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$. The left plot shows the average domain size $L_1$ obtained from the spherically averaged structure factor. The right plot shows the parallel and perpendicular domain size obtained from the respective second moments of the 3D structure factor. Errorbars indicate the standard deviation taken over three independent simulation runs. For anisotropic particles, the directional domain size becomes more anisotropic with increasing field strength.}
\label{fig:D2a_B}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/tortuosity_compare.png}
\caption{Dependence of the tortuosity on the magnetic field strength $\bar{B}$ for different particle shapes $\alpha$. 
Different components of the tortuosity tensor show the anisotropy for oblate and prolate particles.}
\label{fig:tau_B}
\end{figure*}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{figures/results/paper1/curvature-vs-B_ss.png} 
    \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
            $\langle K \rangle \Sigma^{-2}$ curvature in the left and right respectively. Each 
            plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ 
            at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
            We observe that the mean curvature does not demonstrate any trends, while the Gaussian 
            curvature shows a reduction as the magnetic field strength is increased for 
            ellipsoidal particles.} 
    \label{fig:curvature-vs-B_ss}
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{figures/results/paper1/genus_curvature_vs_coverage.png} 
    \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
    From left to right, we have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, we see a 
    magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
    occurs when ellipsoidal particles are used but not spherical particles.} 
    \label{fig:curvature_vs_coverage}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/S-vs-t.png}
\caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) 
        particles at different field strength $\bar{B}$. Errorbars indicate the standard deviation taken over 
        three independent simulation runs. Nematic order generally increases with applied field strength for all particle geometries. 
        The increase slows down (for prolate particles) or reverses (for oblate particles) around $10^4$ timesteps.}
\label{fig:nematic_time}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/results/paper1/interface_nematic.png}
\caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
\label{fig:interface_nematic}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/psi-vs-t.png}
\caption{Time-dependence of the average angle $\psi$ between the particle axis and the 
        interface normal for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different 
        magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three 
        independent simulation runs. The angle between between the particles and the interface normal generally 
        approaches the energetically preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles).
        The average angle changes most rapidly around $10^4$ timesteps.}
\label{fig:psi_time}
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
    \caption{Time dependence of the mean six fold symmetry parameter, $\langle Q6 \rangle$ for bijels 
    stabilized with oblate(left), spherical(middle) and prolate(right) particles. We show that spherical 
    particles posess the hexagonal close packing structure for particles on interfaces. Ellipsoidal particles 
    however posess behavior that is magnetic field and particle aspect ratio dependent.} 
    \label{fig:Q6_coverage} 
\end{figure}

>>>>

\section{Introduction}

@@

\begin{figure}
\centering
\includegraphics[scale = 0.4]{figures/results/paper1/D2a-vs-B_ss.png}
\caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$. The left plot shows the average domain size $L_1$ obtained from the spherically averaged structure factor. The right plot shows the parallel and perpendicular domain size obtained from the respective second moments of the 3D structure factor. Errorbars indicate the standard deviation taken over three independent simulation runs. For anisotropic particles, the directional domain size becomes more anisotropic with increasing field strength.}
\label{fig:D2a_B}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[scale = 0.4]{figures/results/paper1/tortuosity_compare.png}
\caption{Dependence of the tortuosity on the magnetic field strength $\bar{B}$ for different particle shapes $\alpha$. 
Different components of the tortuosity tensor show the anisotropy for oblate and prolate particles.}
\label{fig:tau_B}
\end{figure*}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale = 0.4]{figures/results/paper1/curvature-vs-B_ss.png} 
    \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
            $\langle K \rangle \Sigma^{-2}$ curvature in the left and right respectively. Each 
            plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ 
            at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
            We observe that the mean curvature does not demonstrate any trends, while the Gaussian 
            curvature shows a reduction as the magnetic field strength is increased for 
            ellipsoidal particles.} 
    \label{fig:curvature-vs-B_ss}
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale = 0.4]{figures/results/paper1/genus_curvature_vs_coverage.png} 
    \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
    From left to right, we have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, we see a 
    magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
    occurs when ellipsoidal particles are used but not spherical particles.} 
    \label{fig:curvature_vs_coverage}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale = 0.4]{figures/results/paper1/S-vs-t.png}
\caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) 
        particles at different field strength $\bar{B}$. Errorbars indicate the standard deviation taken over 
        three independent simulation runs. Nematic order generally increases with applied field strength for all particle geometries. 
        The increase slows down (for prolate particles) or reverses (for oblate particles) around $10^4$ timesteps.}
\label{fig:nematic_time}
\end{figure}

@@

\begin{figure}
\includegraphics[scale = 0.4]{figures/results/paper1/interface_nematic.png}
\caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
\label{fig:interface_nematic}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale = 0.4]{figures/results/paper1/psi-vs-t.png}
\caption{Time-dependence of the average angle $\psi$ between the particle axis and the 
        interface normal for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different 
        magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three 
        independent simulation runs. The angle between between the particles and the interface normal generally 
        approaches the energetically preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles).
        The average angle changes most rapidly around $10^4$ timesteps.}
\label{fig:psi_time}
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
    \caption{Time dependence of the mean two and six fold symmetry parameter, $\langle Q2 \rangle$ and $\langle Q6 \rangle$ 
    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. We use $\langle Q2 \rangle$ as an
    indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
    \label{fig:Q6_coverage} 
\end{figure}
